---
title: "HDAT9600 Team Based Learning Activity"
subtitle: "TBLA 3. Linear models 2"
author: "Mark Hanly"
date: "08 Mar 2022"
output: github_document
---

```{r setup, include=FALSE}
# leave this code here, but feel free to adjust the options or add some more
# see the knitr documentation for details
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(emo)
```

### Housekeeping

`r emo::ji("video")` Cameras and recording 

`r emo::ji("computer")` Linear models assessment open. Due 9am Monday 14 March.

`r emo::ji("thinking")` Follow up on questions from last week

***

### TBLA Submissions

#### `r emo::ji("party")` Lot's of great work---well done!

Let's discuss.


## Introduction

In this task, you will use a dataset called `tvdoctor` which is contained in the _faraway_ package for R which you should already have installed. If not, install it now using the Packages tab in RStudio or the `install.packages()` function at R console prompt.

The origins of this dataset are unknown, and therefore its veracity should be viewed with some suspicion, but it purports to contain data collected in 1993 for life expectancy (the `life` variable), the number of people per television set `tv`, and the number of people per doctor `doctor` in 38 different countries. Obviously this is a rather inadequate dataset, even if the data are real, but it is useful for teaching purposes.

## Accessing the data

We can use the `data()` function from the `utils` package to load the data into the R environment, and the `head()` function to take a sneak peek.

```{r}
data(tvdoctor, package = "faraway")
head(tvdoctor)
```


## Instructions

1. Fit a linear regression model to the `tvdoctor` dataset using `life` as the outcome (response) variable and the other two variables as predictors. Print the model summary and provide a brief interpretation for the model estimates.
1. Check the normality assumption for the errors using plots and/ or statistical tests. Discuss on what you find.
1. Check the constant variance assumption for the errors using plots and/ or statistical tests. Discuss on what you find.

_**Note that we will discuss your findings and interpretation in the online tutorial**_

## Sample Submission

### 1. Fit a linear regression model to the `tvdoctor` dataset using `life` as the outcome (response) variable and the other two variables as predictors. Print the model summary and provide a brief interpretation for the model estimates.

The model results are presented below. 

```{r}
mod1 <- lm(life~tv + doctor, data = tvdoctor)
ci <- confint(mod1)

summary(mod1)
ci

```

_*How do we interpret these? Write down a sentence for the interpretation of the tv parameter*_

### 2. Check the normality assumption for the errors using plots and/ or statistical tests. 

```{r}
tvdoctor$p <- predict(mod1)
tvdoctor$e <- tvdoctor$life - tvdoctor$p

ggplot(data = tvdoctor, aes(x=e)) + geom_histogram(bins=8) + labs(title = "histogram of residuals")

ggplot(data = tvdoctor, aes(sample = p)) + geom_qq() + geom_qq_line() + labs(title = "QQ plot of residuals")

```

_**So how do we feel about these?**_

We can also test this formatlly with the Shapiro-Wilks test:

```{r echo=TRUE}
shapiro.test(tvdoctor$e)
```

For this test the null hypothesis is that the residuals are normal. The p-value is relatively high so we do not reject this hypothesis. That’s not to say that the residuals are perfectly normally distributed, just that there is not sufficient statistically-significant evidence to conclude that they are not normal.


### Check the constant variance assumption for the errors using plots and/ or statistical tests. 

```{r}

ggplot(tvdoctor, aes(x = p, y = e)) + geom_point() + geom_hline(yintercept = 0, color = 'red') + labs(title = "Plot of residuals against estimated values")

```

_**How do we feel about these?**_

We can also perform a statistical test to test for non-constant variance with the Breusch-Pagan test. 

```{r echo = TRUE}
# Breusch-Pagan test from olsrr library
olsrr::ols_test_breusch_pagan(mod1, rhs=TRUE)
```

The null hypothesis for this test is that the variance is constant. The p-value is relatively high so we do not reject this null hypothesis. 

***

